---
title: "Co2 Prediction"
subtitle: "(Data Products Course)"
author: "Massoud Mazar"
date: "October 8, 2017"
output: slidy_presentation
framework: html5slides
mode: selfcontained
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(xtable)
```

## Why Co2 Prediction
Want to predict amount of Co2 emission produced from your road trip? You can use Co2 Predictor!
You only need to know fuel type and engine capacity of the vehicle and this app gives you amount of Co2 produced per kilometer traveled.

## Supported Fuel Types

Following fuel types are supported:

```{r cars, echo = FALSE, results='asis'}
data <- read.csv("data.csv")
fuelTypes <- data.frame(unique(data$Fuel.Type))
print(xtable(fuelTypes), type = "html")
```

## Our Models

We use linear models for our predictions. This plot shows how our models fit our traning data:

```{r pressure}
qplot(Engine.Capacity, Co2, data = data, color = Fuel.Type) + geom_smooth(method = "lm")
```

## Refrences

We use data from this source for creating our models:
https://www.kaggle.com/dananos/car-emissions-data